---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# QQreflimits

<!-- badges: start -->
<!-- badges: end -->

The goal of QQreflimits is to provide routines for finding reference limits using, where appropriate, QQ methodology.  All use a data vector X of cases from the reference population.  The default is to get the central 95% reference range   of the population, namely the 2.5 and 97.5 percentiles.  

   * In some settings we want the 99% range. 
   * Sometimes we want only one of these limits – for example the upper 95% point.  
   * Along with the reference limit, we want a confidence interval which, 
   for historical reasons, is typically at 90% confidence.  A full analysis 
   provides six numbers:

      * the upper and the lower reference limits, and 
      * each of their confidence intervals.

## Installation

You can install the development version of QQreflimits like so:

``` r
install.packages("QQreflimits")  # once available on CRAN
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, fig.height=8}
library(QQreflimits)

# parameters
mu    <- 40
sigma <- 10
n     <- 120
# identifying winsoring
wins  <- trunc(n/40)
# replicable randomization
set.seed(1069)
X     <- mu + sigma*rnorm(n)
# replicable randomization with heavy tails
set.seed(1069)
HT    <- mu + sigma * rt(n, 5)

# visual settings
par(mfrow=c(2,2))
par(oma=c(0,0,2,0))
# plot to compare
base <- QQnorm(X, main="Base normal", showsum=TRUE)
title("Illustrating QQnorm with para_limits", outer=TRUE)
basew <- QQnorm(X, main="Winsorized", winsor=wins, showsum=TRUE)
ht   <- QQnorm(HT, main="Heavy tail", showsum=TRUE)
htw  <- QQnorm(HT, main="Winsorized", winsor=wins, showsum=TRUE)

# evaluate and review
norm_results <- para_limits(mean(X), sd(X), n)
norm_results
# evaluate and review with tails
tailed_results <- para_limits(htw$intercept, htw$slope, n, winsor=wins)
tailed_results
```
